\ieeetitle

### 2017-02-06 report/introduction.tex
Change cluster parameters to evaluation section
Correct typos in report

Creating an algorithm providing scalability, integrity and validity, along with a total ordering of the events through all peers in a distributed network has been one the hot topics in distributed computing research for many years. There are many algorithms for disseminating and ordering events in a distributed network. There are deterministic algorithms, which guarantee total order, agreement or other strong properties. Unfortunately, these types of algorithms are not scalable enough to be used in large-scale distributed systems \autocites[]{defago2004total}[]{lamport1978time}.
\par
The problem with existing deterministic total ordering protocols is that they need some sort of agreement between all peers in the network. This causes a massive amount of network traffic and overhead on the system.
Moreover, an agreement feature for an asynchronous system requires to
explicitly maintain a group and have access to a failure detector \autocites[]{chandra1996weakest}[]{chandra1996unreliable}. Due to faults and churn in large-scale distributed systems, the failure detector turns into a bottleneck for the structure and thus limits the algorithm's scalability.
\par
As an alternative to deterministic algorithms, there are probabilistic algorithms, focusing on scalability and resiliency against failures using a probabilistic dissemination approach  \autocite{birman1999bimodal,carvalho2007emergent,demers1987epidemic,eugster2003lightweight,felber2002probabilistic,hayden1996probabilistic,kim2004gossip,Koldehofe02simplegossiping}. These algorithms guarantee the dissemination of events in the system with high probability. This way, there is no need for failure detectors and redundant traffic, making these algorithms highly scalable. As these algorithms focus on reliability of dissemination, they often have to ignore other properties such as total ordering.

@@

By using a probabilistic dissemination together with deterministic ordering, \epto provides total order along with scalability, validity and integrity. \epto consists of two distinct components. \epto's dissemination component guarantees that all peers will receive an event with arbitrarily high probability. Once peers have received all events, \epto's ordering component orders them using the events timestamp, and in case of a tie use the broadcaster ID of the events.

@@

Using the balls-and-bins approach we model processes as bins and events as balls and calculate how many balls need to be \textit{thrown} such that every bin contains at least one ball with arbitrarily high probability. With this approach the number of messages transmitted per process per round is logarithmic in the number of processes, therefore the number of messages sent in the system is low and uniform over all processes. Thanks to these approaches, \epto is highly resilient with  imperfect networks and highly scalable as the networks grow, while always providing total order.

>>>>

Creating an algorithm providing scalability, integrity and validity, along with a total ordering of the events through all peers in a distributed network has been one the hot topics in distributed computing research for many years. There are many algorithms for disseminating and ordering events in a distributed network. There are deterministic algorithms, which guarantee total order, agreement or other strong properties. Unfortunately, these types of algorithms are not scalable enough to be used in large-scale distributed systems \autocites[]{defago2004total}[]{lamport1978time}.
\par
The problem with existing deterministic total ordering protocols is that they need some sort of agreement between all peers in the network. This causes a massive amount of network traffic and overhead on the system.
Moreover, an agreement feature for an asynchronous system requires to
explicitly maintain a group and have access to a failure detector \autocites[]{chandra1996weakest}[]{chandra1996unreliable}. Due to faults and churn in large-scale distributed systems, the failure detector turns into a bottleneck for the structure and thus limits the scalability of the algorithm.
\par
As an alternative to deterministic algorithms, there are probabilistic algorithms, focusing on scalability and resiliency against failures using a probabilistic dissemination approach  \autocite{birman1999bimodal,carvalho2007emergent,demers1987epidemic,eugster2003lightweight,felber2002probabilistic,hayden1996probabilistic,kim2004gossip,Koldehofe02simplegossiping}. These algorithms guarantee the dissemination of events in the system with high probability. This way, there is no need for failure detectors and redundant traffic, making these algorithms highly scalable. As these algorithms focus on reliability of dissemination, they often have to ignore other properties such as total ordering.

@@

By using a probabilistic dissemination together with deterministic ordering, \epto provides total order along with scalability, validity and integrity. \epto consists of two distinct components. \epto's dissemination component guarantees that all peers will receive an event with arbitrarily high probability. \epto's ordering component works alongside the dissemination component and orders the received events using their timestamp, and in case of a tie use the broadcaster ID attached to them.

@@

Using the balls-and-bins approach we model processes as bins and events as balls and calculate how many balls need to be \textit{thrown} such that every bin contains at least one ball with arbitrarily high probability. With this approach the number of messages transmitted per process per round is logarithmic in the number of processes, therefore the number of messages sent in the system is low and uniform over all processes. Thanks to these approaches, \epto is highly resilient with  imperfect networks and highly scalable as the network grow, while always providing total order.
